Local Spectral Clustering of Density Upper Level Sets

### 2021-09-01 jmlr/revision2/appendix.tex
Added plots to new folder.

\begin{figure}
	\centering
	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{../row4_true_density_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{../row4_ppr_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{../row4_conductance_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{../row4_density_cluster}
			\caption{}
		\end{subfigure}
		\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
			cut (column 3) and estimated density (column 4) clusters for two-moons with 10 dimensional noise. Seed node for PPR denoted by a black cross.} 
		\label{fig:moons_hd}
	\end{adjustbox}
\end{figure}

>>>>

\begin{figure}
	\centering
	\begin{adjustbox}{minipage=\linewidth,scale=0.8}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{plots/experiment_2/row4_true_density_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{plots/experiment_2/row4_ppr_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{plots/experiment_2/row4_conductance_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{plots/experiment_2/row4_density_cluster}
			\caption{}
		\end{subfigure}
		\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
			cut (column 3) and estimated density (column 4) clusters for two-moons with 10 dimensional noise. Seed node for PPR denoted by a black cross.} 
		\label{fig:moons_hd}
	\end{adjustbox}
\end{figure}
